On the Cram\'{e}r-Rao bound for polynomial phase signals

### 2013-03-13 paper.tex
put figures on individual pages

\documentclass[preprint,10pt]{elsarticle}
%\documentclass[review]{elsarticle}
%\documentclass[5p]{elsarticle}

@@

Polynomial-phase signals have applications including radar, sonar, biology, and radio communication~\cite{Angeby_estimating_2000,Levanon_Radar_signals_2004,gershman_estimating_2001}.  %The signals are also used to describe the sounds emitted by bats for echo-location \cite{Peleg_DPT_1995,Moss_2005echolocation,Suga_1975_bats_echolocation}.  
Of practical importance is the estimation of the coefficients $\beta = (\beta_0, \dots \beta_m)\in\reals^{m+1}$ from $N$ consecutive samples $y_1, \dots, y_N$ where 
\begin{equation}\label{eq:yndatamodel}
y_n = s_n(\beta) + w_n
\end{equation}
and $\{w_n, n \in \ints\}$ is a sequence of noise variables.  Many estimators have been studied and implemented~\cite{Oshea_cpf_2004,Morelande_bayes_unwrapping_2009_tsp,Kitchen_polyphase_unwrapping_1994,Angeby_estimating_2000,Peleg_DPT_1995, Djuric_phase_unwrap_chirp_1990}.

@@

>>>>

%\documentclass[preprint,10pt]{elsarticle}
\documentclass[review]{elsarticle}
%\documentclass[5p]{elsarticle}

@@

Polynomial-phase signals have applications including radar, sonar, biology, and radio communication~\cite{Angeby_estimating_2000,Levanon_Radar_signals_2004}.  %The signals are also used to describe the sounds emitted by bats for echo-location \cite{Peleg_DPT_1995,Moss_2005echolocation,Suga_1975_bats_echolocation}.  
Of practical importance is the estimation of the coefficients $\beta = (\beta_0, \dots \beta_m)\in\reals^{m+1}$ from $N$ consecutive samples $y_1, \dots, y_N$ where 
\begin{equation}\label{eq:yndatamodel}
y_n = s_n(\beta) + w_n
\end{equation}
and $\{w_n, n \in \ints\}$ is a sequence of noise variables.  Many estimators have been studied and implemented~\cite{Oshea_cpf_2004,Morelande_bayes_unwrapping_2009_tsp,Kitchen_polyphase_unwrapping_1994,Angeby_estimating_2000,Peleg_DPT_1995, Djuric_phase_unwrap_chirp_1990}.

@@

\clearpage
